Group 2 Final Project Report

### 2013-12-19 reportLatex/paper.tex
final report and presentation

In our original project proposal we expressed our intent to use a high-level synthesis tool to a convert a C implementation of the SHA-1 algorithm directly into VHDL.  We were then going to compare our hand-coded core against the synthesized version to determine how it compared in terms of performance and resource utilization.  In our proposal we listed two tools:  Xilinx HLS and Jacquard ROCCC 2.0.  in the course of working on this project we discovered that the university did not have a license for Xilinx HLS.  We were not inclined to purchase a license ourselves for a single project (about \$2000).  This left the ROCCC 2.0 compiler.  Although the ROCCC web-site is operational, the project itself appears to be either defunct or the administrators are uninterested in responding to students.  All inquires to get a student license for the ROCCC 2.0 compiler went unanswered.
\section{Conclusion}
The implementation of a PL SHA1 cryptographic algorithm using the Linux kernel Crypto API was shown to be successful.  This involved customizations to the Linux operating system, generated logic, as well as a open source algorithm core.  The design was validated initially through simulation and at completion through software testing.
Upon examining the waveforms in the simulation we discovered the process time in the SHA1 core could be optimized a bit more by using a wider AXI bus to send more than one 32 bit word at a time for more parallelized processing.  With the limitation hinging on the fact SHA1 is a block algorithm and limited by the serialized 64byte hash step.
With a successful implementation of a software simulated SHA1 we moved to a hardware implementation on a Zynq board.  We used the same approach as the software validation and stepped through tests to verify that all pieces were working properly with the final test being a multi block message being passed through the core and validated on the output.  This proved to be successful in the end, but has significant performance depreciation in speed.  We attributed this to the 50 MHz clock signal on the Zynq board and AXI bus to the ARM core while the software version ran a 1 GHz clock signal and all three pieces were in phase on the clock signal.  We achieved all middle level milestones for the project while discovering several areas for future development and extended data for this report.

>>>>

In our original project proposal we expressed our intent to use a high-level synthesis tool to a convert a C implementation of the SHA-1 algorithm directly into VHDL.  We were then going to compare our hand-coded core against the synthesized version to determine how it compared in terms of performance and resource utilization.  In our proposal we listed two tools:  Xilinx HLS and Jacquard ROCCC 2.0.  in the course of working on this project we discovered that the university did not have a license for Xilinx HLS.  We were not inclined to purchase a license ourselves for a single project (about \$2000).  This left the ROCCC 2.0 compiler.  Although the ROCCC web-site is operational, the project itself appears to be either defunct or the administrators are uninterested in responding to students.  All inquires to get a student license for the ROCCC 2.0 compiler went unanswered.
\section{Conclusion}
This project implemented the SHA-1 hash algorithm on a SoC FPGA (Xilinx Zynq).  To create our implementation, we used open-source user space applications, new Linux drivers, and combination of customized open-source and generated programmable logic.  Validation of the design occurred during its development, and consisted of both ModelSim simulation and software testing on the Zynq development kit.

While we successfully created a working implementation, and thus satisfied all of our middle-level objectives, our FPGA implementation was shown to perform significantly slower than a pure software based SHA-1 algorithm.  This performance difference can be attributed to properties of the SHA-1 algorithm itself, the faster clock rate of our CPU, and our FPGA’s I/O design.  This report outlines several enhancements that could be implemented to improve hashing on the FPGA.
